Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal

### 2010-01-20 doc/msc-proposal/msc-proposal.tex
proposal: added abstract

%% Abstract page
\newpage
\begin{abstract}
Abstract
\end{abstract}

>>>>

%% Abstract page
\newpage
\begin{abstract}
IEEE 802.15.4 is a standard which specifies the physical layer and media access control for low-rate wireless personal area networks providing node-to-node frame delivery between devices within reachable distance. The standard is targeted at low-cost, low-speed and low-power devices. Simple Network Management Protocol (SNMP) is a widely deployed application protocol for network management and data retrieval. It can be very lightweight and may fit resource-constrained devices very well. The focus of the proposed work will be implementation and evaluation of the SNMP protocol for devices supporting IEEE 802.15.4 Radios and the Contiki Embedded Operating System. This document provides background information on several related areas, such as 802.15.4 standard,                          the 6LoWPAN approach for transmitting IPv6 traffic over 802.15.4 and the SNMP protocol.

\end{abstract}
